Genetic Algorithm Based Formula Generation for Curve Fitting in Time Series Forecasting Implemented as Mobile Distributed Computing

### 2019-09-01 Genetic-Algorithm-Based-Formula-Generation-for-Curve-Fitting-in-Time-Series-Forecasting-Implemented-as-Mobile-Distributed-Computing/presentation.tex
Final corrections.

\begin{frame}
\frametitle{Time Series Forecasting}
\begin{itemize}
	\item It is applicable in processes with clear repetition pattern
	\item Measurements done in a temporal order are presented as points in a two-dimensional space
	\item Visually these points are connected with straight lines (simplified form of linear interpolation for the values between two neighboring measurements)
	\item In such two-dimensional space many different curves can be proposed for some generalization of the data nature (curve fitting problem)
	\begin{itemize}
		\item Linear regression can be used for trend estimation
		\item Lagrange polynomial as more complex generalization
	\end{itemize}
\end{itemize}
{\color{red} Infinite number of curves can satisfy the condition to pass across finite number of points in two-dimensional space}
\end{frame}

@@

\begin{frame}
\frametitle{Distribution of Computations}
\begin{itemize}
	\item A computational organization in a system where components are located on different networked computers
	\item Computers communicates and coordinates their activities by passing messages between each other
	\item It is remarkable with:
	\begin{itemize}
		\item Concurrency of components
		\item Lack of a global clock
		\item Independent failure of components
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Mobile Distributed Computing}
\begin{itemize}
	\item Modern mobile devices have significant computation capabilities
	\item Most of the mobile devices are operating 24x7
	\item Active wallpaper is used instead screen-saver
\end{itemize}
Widgets are also an option, which can extend the idea to human-computer based distributed computing
\end{frame}

@@

\begin{frame}
\frametitle{Keeping Solutions}
\begin{itemize}
	\item Best found local solutions are reported to the remote server
	\item On the remote server global population is kept
	\item When new mobile client is connected subset of the global population is sent as new local population
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Disadvantages}
\begin{itemize}
	\item Formulas generation is time consuming process
	\item Financial time series are not constant they are evolving
	\begin{itemize}
		\item Need of recalculation with the time passing
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Questions and Answers}
\center \huge{Thank you for the attention!}
\end{frame}

>>>>

\begin{frame}
\frametitle{Time Series Forecasting}
\begin{itemize}
	\item It is applicable in processes with clear repetition pattern
	\item Measurements done in a temporal order are presented as points in a two-dimensional space
	\item Visually, these points are connected with straight lines (simplified form of linear interpolation for the values between two neighboring measurements)
	\item In such two-dimensional space many different curves can be proposed for some generalization of the data nature (curve fitting problem)
	\begin{itemize}
		\item Linear regression can be used for trend estimation
		\item Lagrange polynomial as more complex generalization
	\end{itemize}
\end{itemize}
{\color{red} Infinite number of curves can satisfy the condition to pass across finite number of points in two-dimensional space}
\end{frame}

@@

\begin{frame}
\frametitle{Distribution of Computations}
\begin{itemize}
	\item A computational organization in a system where components are located on different networked computers
	\item Computers communicate and coordinate their activities by passing messages between each other
	\item It is remarkable with:
	\begin{itemize}
		\item Concurrency of components
		\item Lack of a global clock
		\item Independent failure of components
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Mobile Distributed Computing}
\begin{itemize}
	\item Modern mobile devices have significant computation capabilities
	\item Most of the mobile devices are operating 24x7
	\item Active wallpaper is used instead of screen-saver
\end{itemize}
Widgets are also an option, which can extend the idea to human-computer based distributed computing
\end{frame}

@@

\begin{frame}
\frametitle{Keeping Solutions}
\begin{itemize}
	\item Best found local solutions are reported to the remote server
	\item On the remote server global population is kept
	\item When new mobile client is connected subset of the global population is sent as a new local population
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Disadvantages}
\begin{itemize}
	\item Formulas generation is time consuming process
	\item Financial time series are not constant they are constantly evolving
	\begin{itemize}
		\item Need of recalculation with the time passing
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Questions and Answers}
\center \huge{Thank you for your attention!}
\end{frame}
